The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-08-21 sections/results.tex
Update figures to new simu and extent offset range

As we aim to model an ice sheet approaching LGM size, and consider temperature offset as an unknown parameter in this study, we ran simulations using offset values ranging from 2 to 9\degC for each climate forcing.

Figure~\ref{fig:extent} shows the extent of ice cover at the end of each of these~(48) simulations, grouped by climate forcing. It is again visible that different forcings generally lead to very different final ice cover. Notably, for the smallest temperature offset value of 2\degC that was used, NCAR and CFSR simulations lead to an ice-sheet, whereas WorldClim, NARR and ERA-Interim produced local ice caps only, restricted to the Wrangell-St.~Elias mountains in the case of WorldClim, an area presently glaciated. Several of the NCAR and CFSR simulations produced oversized ice-sheets whose extent is primirily bounded by the model domain boundary conditions rather than physical processes. Differences in regional patterns can also be noted. For instance ERA-Interim ice sheets generally appear more northernly-centered than NARR ice sheets.

>>>>

As we aim to model an ice sheet approaching LGM size, and consider temperature offset as an unknown parameter in this study, we ran simulations using offset values ranging from 0 to 15\degC for each climate forcing.

Figure~\ref{fig:extent} shows the extent of ice cover at the end of each of these~(96) simulations, grouped by climate forcing. It is again visible that different forcings generally lead to very different final ice cover. Notably, for the smallest temperature offset value of 2\degC that was used, NCAR and CFSR simulations lead to an ice-sheet, whereas WorldClim, NARR and ERA-Interim produced local ice caps only, restricted to the Wrangell-St.~Elias mountains in the case of WorldClim, an area presently glaciated. Several of the NCAR and CFSR simulations produced oversized ice-sheets whose extent is primirily bounded by the model domain boundary conditions rather than physical processes. Differences in regional patterns can also be noted. For instance ERA-Interim ice sheets generally appear more northernly-centered than NARR ice sheets.
